---
title: "Visualization 1"
author: "ke"
date: "10/5/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
```

# Visulization 1

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```


## Scatterplots!

Create my first scatterplot ever.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))+
  geom_point()
```

New approach, same plot.

```{r}
weather_df %>%
  # here can also add mutate, select or ...
  ggplot(aes(x = tmin, y = tmax))+
  geom_point()
```

Save and edit a plot object.

```{r}
weather_plot = 
  weather_df%>%
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced sactterplot

Start with the same one and make it fancy

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE) # always false, 不用管; smooth: a smooth curve
```

What about the `aes` placement..?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()

#here only a blue smooth line appears, better to put those in ggplot, or your command can pass on 
```

Let's facet some things!

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_grid(. ~name) #. means don't rows, define name in columns

weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + #alpha = tmin, tmin 由浅变深
  geom_point(alpha = .5, size = .3) +
  geom_smooth(se = FALSE, size = 2) +
  facet_grid(name~ .)
```

Let's combine some elements and try a new plot.

```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) + # 圆点由小变大
  geom_smooth(se = FALSE) +
  facet_grid(. ~name)
```


## Some small notes

How many geoms have to exist?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE) # with no data points
```

You can use a neat geom.

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex() #蜂巢样子的data point
```

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density_2d() # a contour
```


## Univariate plots

Histograms are really great.

```{r}
weather_df %>%
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color...
```{r}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = "dodge") # make bar not overlap, or you can use facet_grid(. ~name)
```

Let's try a new geometry.

```{r}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3, adjust = .5) # look like a probably density, if add adjust function, look more detailed
```

What about box plots?

```{r}
weather_df %>%
  ggplot(aes(x = name,y = tmin)) +
  geom_boxplot()
```

Trendy plots

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin()
```

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) +
  stat_summary(fun = "median")
```

Ridge plots -- the most popular plot of 2017

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```


## Save and Embed

Let's save a scatterplot.

```{r}
weather_plot =
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("./results/weather_plot.pdf", weather_plot, width = 8, height = 5)
```

What about embedding.

```{r, fig.width= 6, fig.height=3}
weather_plot
```

A different size
```{r, fig.width= 12, fig.height=6}
weather_plot
```


# Visulization II

## Remember this plot..?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)
```

## Adding  labels

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package; temoerature in 2017."
  )
```

## Scales

Start with the same plot

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package; temoerature in 2017."
  ) +
  scale_x_continuous(
    breaks = c(-15, 0, 15),
    labels = c("-15 C", "0", "15")
  ) +
  scale_y_continuous(
    trans = "log", #transform y value into log(y)
    position = "right" # label in right
  )
```

Look at color scales

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package; temoerature in 2017."
  ) +
  scale_color_hue(
    name = "Location", # change name of coloe label
    h = c(100,300))
```

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package; temoerature in 2017."
  ) +
  viridis::scale_color_viridis(
    name = "Location",
    discrete = TRUE)
```

## Themes

Shfit the legend
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package; temoerature in 2017."
  ) +
  viridis::scale_color_viridis(
    name = "Location",
    discrete = TRUE) +
  theme(legend.position = "bottom") # move color legend into bottom
```

Change the overall theme
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package; temoerature in 2017."
  ) +
  viridis::scale_color_viridis(
    name = "Location",
    discrete = TRUE) +
  theme_minimal() # change background of plot
```


## Setting options

画图模板, what you should include when plotting
```{r, eval=FALSE}

library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom")) # always keeping it at the last line of code

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d # these four line is to make sure all plot are using "viridis" color
```


## Data args in `geom`

```{r}
central_park = 
  weather_df %>%
  filter(name == "CentralPark_NY")

waikiki = 
  weather_df %>%
  filter(name == "Waikiki_HA")

ggplot(data = waikiki, aes(x = date, y = tmax, color = name)) +
  geom_point() +
  geom_line(data = central_park) #you can call different data
```


## Patchwork

Remember faceting?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .5) +
  facet_grid(. ~name)
```

What happens when you want multipanel plots but can't facet...?

```{r}
tmax_tmin_p = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  theme(legend.position = "none")

prcp_dens_p =
  weather_df %>%
  filter(prcp > 0) %>%
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha = .5) +
  theme(legend.position = "none")

tmax_date_p =
  weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  theme(legend.position = "none")

tmax_tmin_p + prcp_dens_p  # you got two side by side plots
(tmax_tmin_p + prcp_dens_p) / tmax_date_p #上面两张，下面一张
```

## Data manipulation

Control your factors
```{r}
weather_df %>%
  mutate(
    name = factor(name),
    name = forcats::fct_relevel(name, c("Waikiki_HA")) # relevel names, change Waikiki as the fitst order
  ) %>%
  ggplot(aes(x = name, y = tmax, color = name)) +
  geom_violin(alpha = .5)
```

What if I wanted densities for tmin and tmax simultaneously?

```{r}
weather_df %>% 
  pivot_longer(
    tmax:tmin,
    names_to = "observation",
    values_to = "temperatures"
  ) %>% 
  ggplot(aes(x = temperatures, fill = observation)) +
  geom_density(alpha = .5) +
  facet_grid(. ~name)
```

Another example:
```{r}
pulse_df = 
  haven::read_sas("data/public_pulse_data.sas7bdat") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit",
    values_to = "bdi",
    names_prefix = "bdi_score_"
  ) %>% 
  mutate(visit = recode(visit, "bl" = "00m"))

pulse_df %>% 
  ggplot(aes(x = visit, y = bdi)) +
  geom_point(size = .2) +
  geom_line(aes(group = id)) # this shows what happens to individuals over time
```


# EDA

```{r}
weather_df =  
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10,
    month = lubridate::floor_date(date, unit = "month")) %>%
  select(name, id, everything())
```



## Group by 
```{r}
weather_df %>% 
  group_by(name) # showing the number of name category above data set, if group_by(month, name), it will show # of groups rise from name and month (两两一组)
```

## count some things

```{r}
weather_df %>% 
  group_by(name, month) %>% 
  summarize(n_obs = n()) #how many observations

weather_df %>% 
  count(name) #和上面的name的结果一样的
```

It's nice that this is a data frame

```{r}
weather_df %>% 
  janitor::tabyl(month, name)

weather_df %>% 
  pull(name) %>% 
  table()  #similar result as above code
```


## More general summaries

Let's count, take means, look at SDs...

```{r}
weather_df %>%
  group_by(name) %>%
  summarize(
    n_obs = n(),
    mean_tmax = mean(tmax, na.rm = TRUE),
    sd_tmax = sd(tmax, na.rm = TRUE),
    median_tmax = median(tmax, na.rm = TRUE)
  ) %>% 
  ggplot(aes(x = month, y = mean_tmax, color = name)) +
  geom_point() +
  geom_line()
```

# Formatting table outputs

```{r}
weather_df %>% 
  group_by(name) %>% 
  summarize(
    n_obs = n(),
    mean_tmax = mean(tmax, na.rm = TRUE)
  ) %>% 
  knitr::kable(digits = 2)
```


## grouped "mutate"

```{r}
weather_df %>%
  group_by(name) %>% #有这一行和没有这一行，跑出来的结果是不一样的
  mutate(
    mean_tmax = mean(tmax, na.rm = TRUE)
  )
```


```{r}
weather_df %>% 
  group_by(name) %>% 
  mutate(
    tmax_rank = min_rank(tmax) # rank, same category having same number
  ) %>% 
  filter(tmax_rank < 2)
```

Lagged variables
```{r}
weather_df %>% 
  group_by(name) %>% 
  mutate(
    lagged_tmax = lag(tmax, n = 1), #this shows what is the tmax on the day before, if there is no group_by(name), it will not lag by name
    tmax_diff = tmax - lagged_tmax
  ) %>% 
  summarize(diff_sd = sd(tmax_diff, na.rm = TRUE))
```

## Limitations

What if my "summary" is a linear model...

```{r, eval=FALSE}
weather_df %>% 
  group_by(name) %>% 
  summarize(cor_tmin_tmax = cor(tmin, tmax, use = "complete")) # find correlation

weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  lm(tmax~tmin, data =.) # regress a model

weath %>% 
  group_by(name) %>% 
  summarize(lm = lm(tmax, tmin,))
```



















