---
title: "Visualization 1"
author: "ke"
date: "10/5/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```


## Scatterplots!

Create my first scatterplot ever.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))+
  geom_point()
```

New approach, same plot.

```{r}
weather_df %>%
  # here can also add mutate, select or ...
  ggplot(aes(x = tmin, y = tmax))+
  geom_point()
```

Save and edit a plot object.

```{r}
weather_plot = 
  weather_df%>%
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced sactterplot

Start with the same one and make it fancy

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE) # always false, 不用管; smooth: a smooth curve
```

What about the `aes` placement..?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()

#here only a blue smooth line appears, better to put those in ggplot, or your command can pass on 
```

Let's facet some things!

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_grid(. ~name) #. means don't rows, define name in columns

weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + #alpha = tmin, tmin 由浅变深
  geom_point(alpha = .5, size = .3) +
  geom_smooth(se = FALSE, size = 2) +
  facet_grid(name~ .)
```

Let's combine some elements and try a new plot.

```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) + # 圆点由小变大
  geom_smooth(se = FALSE) +
  facet_grid(. ~name)
```


## Some small notes

How many geoms have to exist?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE) # with no data points
```

You can use a neat geom.

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex() #蜂巢样子的data point
```

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density_2d() # a contour
```


## Univariate plots

Histograms are really great.

```{r}
weather_df %>%
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color...
```{r}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = "dodge") # make bar not overlap, or you can use facet_grid(. ~name)
```

Let's try a new geometry.

```{r}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3, adjust = .5) # look like a probably density, if add adjust function, look more detailed
```

What about box plots?

```{r}
weather_df %>%
  ggplot(aes(x = name,y = tmin)) +
  geom_boxplot()
```

Trendy plots

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin
```

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) +
  stat_summary(fun = "median")
```

Ridge plots -- the most popular plot of 2017

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```

